|

### 2021-04-02 appendix/appendix.Rmd
changing dataset and appendix new dataset results

Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as proposed by @primo2008distributive. Here, we showed the variation in deadweight losses, but there are many other theoretical reasons, such as the existence of upper houses [@chen_malhotra_2007], the popular initiatives [@XXXX], and XXXX. Most of the literature after @weingast1981political, focused on complement their original formulation.

>>>>

Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as proposed by @primo2008distributive. Here, we showed the variation in deadweight losses, but there are many other theoretical reasons, such as the existence of upper houses [@chen_malhotra_2007], the popular initiatives [@matsusaka2005endogeneity], the type of government [@coate2011government], the existence of supermajorities [@lee2015supermajority], political fragmentation [@lledo2003electoral], ideological positions [@bjedov2014impact], among other characteristics. Most of the literature after @weingast1981political, focused on complement their original formulation.
